---
title: "Polyglot markdown & callr example"s
output: html_notebook
---
```{r setup}
library(tidyverse)
library(callr)
library(DBI)
library(reclues)
```

# Polyglot Markdown!

You can use languages other than R in your code chunks. Python, bash, SQL, Ruby, they're all options!

**R chunk** 
```{r}
# Here's a normal R chunk, setting up a SQL database connection
con <- reclues::get_db()
```

**SQL chunk** 
```{sql comment='--', connection=con}
-- Chunk options: "{sql comment='--', connection=con}"
select * from crime_scene_report limit 2
```

To return the result of a SQL query to your Global Environment, add `output.var="reports"` to the chunk options.

```{sql comment='--', connection=con, output.var="reports"}
select * from crime_scene_report
```

```{r}
str(reports)
```

# Background Jobs

We'll use the `callr` package:

* Your code must be wrapped up as a function using `r_bg()`
* You need to explicity give `r_bg()` anything from the GE that it needs to run
* Capture messages and errors by specifying .err and .out files (optional)
* Running the code chunk submits the job

```{r}
slow_code <- r_bg(function(x) {
  require(magrittr)
  require(dplyr)
  message("Going to wait a bit so we can see the results of $is.alive()")
  Sys.sleep(60)
  
  crime_summary <- x %>% 
    group_by(type) %>% 
    summarize(occurances= n())
  
  return(crime_summary)
  },
args = list(x = reports), #reports is a dataframe in our global environment
stdout = "./tmp/callr_example.out",
stderr = "./tmp/callr_example.err"
  )
```

* Check the status of your job with `$is.alive()`

```{r}
slow_code$is_alive()
```

* Tip: put your job objects in a list and use `purrr:map(job_list, function(x) x$is.alive)` to quickly see how they're all doing

* Once the job is dead (either finished or errored out), use $get_result() to return the result to your environment

```{r}
crime_summary <- slow_code$get_result()

crime_summary
```

* Bonus option: if you want to see if your Notebook will run top to bottom "hands off", put the is_alive() function in a while loop to make the notebook wait until all jobs are done before continuing to run the next chunk. 

```{r}
job_list <- list(slow_code)

# a list of statuses, TRUE = running, FALSE = finished
job_progress <- map(job_list, function(x) x$is_alive())

# count how many are still running (TRUE = 1)
still_running <- Reduce(`+`, job_progress)

# so long as there's 1+ job running, this loop will continue, 
# and the code chunk won't finish
while (still_running > 0) {
  job_progress <- map(job_list, function(x) x$is_alive())
  still_running <- Reduce(`+`, job_progress)
}

```


